---
title: "Datatable Demo"
author: "Shi (Edwin) Bai"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(DT)
```

******
### Cheatsheet
#### Link: https://github.com/eunos2345/R-Datatable/blob/master/DT%20Cheatsheet.pdf

******

### Datatable with Zero Configuration
```{r}
datatable(iris)
```

******

### Datatable with "Compact" and "Hover" sytle
```{r}
datatable(iris, class = "compact hover")
```

******

### Customize Row and Column Names
```{r}
datatable(iris, rownames = FALSE, colnames = c("S-Length"="Sepal.Length", "S-Width"="Sepal.Width", "P-Length"="Petal.Length", "P-Width"="Petal.Width"))
```

******

### Datatable with Caption at the Bottom
```{r}
datatable(iris, caption = htmltools::tags$caption(style = "caption-side: bottom;
           text-align: center;","Iris Table"))
```

******

### Datatable with Column Filters, and *Sepal.Lenght* column Rounded to Integer

```{r}
datatable(iris, filter = "top") %>% formatRound("Sepal.Length",0)
```

******

### Datatable that 
**- Sorted the by column 2 (ascending), and then column 4 (descending)**

**- Disabled sorting for column 3**

**- With displaying 5 rows by default, and the number of rows can be displayed are 5 and 10**

**- Center the elements in the 5th column**

```{r}
datatable(iris, options = list(
  columnDefs = list(
    list(className = 'dt-center', targets = 5),
    list(orderable = FALSE, targets = 3)
  ),
  pageLength = 5,
  lengthMenu = c(5,10),
  order = list(
    list(2, "asc"),
    list(4, "desc")
  ))
)
```

******

Author: Shi (Edwin) Bai, s.bai@columbia.edu

Reference: https://rstudio.github.io/DT/, and https://datatables.net/
